Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-06 article/article.tex
Collision -> timeout trial 2

\begin{table}[]
\centering
\ra{1.3}
\caption{Convergence performance of the robots}
\label{table:convergence}
\begin{tabular}{@{}lllllll@{}}
\toprule
\multirow{2}{*}{Trial} & \multicolumn{3}{c}{Robot 0}       & \multicolumn{3}{c}{Robot 1}      \\ \cmidrule(l){2-4} \cmidrule(l){5-7}
                       & Time (s)  & Distance (cm) & Start & Time (s) & Distance (cm) & Start \\ \midrule
1                      & 213       & 53            & South & 94       & 22            & North \\
2                      & \emph{Collision} & 420           & South & 153      & 36            & North \\
3                      & 308       & 19            & South & 105      & 36            & North \\
4                      & \emph{Collision} & 340           & South & 80       & 20            & North \\
5                      & \emph{Collision} & 240           & South & 92       & 30            & North \\
6                      & 179       & 46            & North & 117      & 20            & South \\
7                      & 56        & 45            & North & 162      & 24            & South \\
8                      & 59        & 27            & North & 197      & 26            & South \\
9                      & 59        & 19            & North & 79       & 30            & South \\
10                     & \emph{Collision} & 231           & North & 67       & 23            & South \\ \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[]
\centering
\ra{1.3}
\caption{Convergence performance of the robots}
\label{table:convergence}
\begin{tabular}{@{}lllllll@{}}
\toprule
\multirow{2}{*}{Trial} & \multicolumn{3}{c}{Robot 0}       & \multicolumn{3}{c}{Robot 1}      \\ \cmidrule(l){2-4} \cmidrule(l){5-7}
                       & Time (s)  & Distance (cm) & Start & Time (s) & Distance (cm) & Start \\ \midrule
1                      & 213       & 53            & South & 94       & 22            & North \\
2                      & \emph{Timeout} & 420           & South & 153      & 36            & North \\
3                      & 308       & 19            & South & 105      & 36            & North \\
4                      & \emph{Collision} & 340           & South & 80       & 20            & North \\
5                      & \emph{Collision} & 240           & South & 92       & 30            & North \\
6                      & 179       & 46            & North & 117      & 20            & South \\
7                      & 56        & 45            & North & 162      & 24            & South \\
8                      & 59        & 27            & North & 197      & 26            & South \\
9                      & 59        & 19            & North & 79       & 30            & South \\
10                     & \emph{Collision} & 231           & North & 67       & 23            & South \\ \bottomrule
\end{tabular}
\end{table}
